Forecasting the old age dependency ratio to determine the best pension age

### 2017-02-08 PensionAge.Rmd
Return trip from Perth

\begin{abstract}
We forecast the old-aged dependency ratio for Australia, and estimate a pension age scheme that will provide a stable old aged dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.

@@

Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the last twenty or so years [@Fehr2008].  Consequently, there are many older people leaving the workforce, and fewer workers replacing them. Similar demographic challenges face many other countries. One way of measuring this problem is via the old-age dependency ratio (OADP): the number of people post-retirement to the number of people of working age [@Walker1982]. The OADP has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.

This is consistent with the Australian Intergenerational Reports [@IGR02; @IGR07; @Swan2010] that explored the extent to which existing age-related policies would affect the burden of future working generations. To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age\footnote{The \textit{pension age} is defined as the age at which eligible residents can access the age pension for the first time.}. In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 [@Nielson2010]. In May 2014, the Federal Treasurer proposed to further increase the pension age to 70 by 2035. This new proposal is in line with the recommendations from the @PC13 and the @NCOA2014. In this paper, we investigate the effect of these changes to the pension age on the forecast OADP.

@@

In this paper, we use the old aged dependency ratio (OADR\footnote{All abbreviations have been summarized in Appendix A.}) as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].  The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age [@ARW07]. This can be expressed using the formula below:
\begin{equation}
  OADR=\frac{\text{number of people aged over pension age}}{\text{number of people aged 15 to pension age}}*100%
\end{equation}
We provide forecasts of future population age structures over the next 50 years. We then use those projections to compute the OADR associated with pension age both before and after the adjustments. One contribution of the current study is the combined use of the Hyndman-Ullah forecasting method [@HU07] and the product-ratio method [@HBY13] to forecast a population age structure.  Forecasts of population structure have been built on forecasts of age and gender-specific mortality rates, fertility rates and net migration using this method. These forecasts presuppose that the historical trends of past years will continue. Historical data of those rates have thus been used as input to simulate future paths of age and gender-specific population structure.

Using these predicted population paths, we can calculate the average of OADR and predict the levels of old age dependency that correspond to different pension age schemes. By testing different pension age schemes, we aim to find the pension age with the desired OADR outcome. Therefore, other contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2) to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at a desired level in the future. It should be noted that the desired level has been set at 21%, which is the estimated current level of OADR in 2014. This level was chosen because, while the current financial burden on tax payers is affordable, it is approaching the limits of affordability. However, whether or not the current level is the most appropriate level to Australia remains to be examined and it is not the focus of this paper. This paper concentrates on providing a framework for policy makers to find a target pension age for a given desired level of OADR.

Some may argue that using OADR as a measure of financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation. However, 80% of Australians over pension age fully or partly rely on the age pension [@Power14]. Therefore, the proportion of people over working age is still a good representation of financial burden on future working generations.  Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors. @HY12 have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance [@HY12]. This paper emphasizes how to undertake a better forecasting of economic burden for a given policy rather than the better choice of measurements. Therefore, the simple version of OADR was chosen to illustrate my approach (i.e., without adjustment). There is a ground to extend the approach to incorporate more complex measurement which takes into account of other important economic factors.

Furthermore, choosing the right model to forecast population age structure was another important step involved in the quantification process. I chose to combine the Hyndman-Ullah method and product-ratio method for the forecast. The combination of those two methods overcomes some of shortcomings of other popular demographic forecasting methods such as the Lee-Carter method [@LC92] or the deterministic methods used by the Australian Bureau of Statistics [@ABS06; @ABS12]. More details on forecasting methods are given in later sections.

The empirical analysis presented in this paper shows the adjustment of the pension age announced in 2009 was effective in reducing the financial burden to the desired level, which was set at current OADR-21%. However, it has been argued that a one-time adjustment is not sufficient to ensure a stable OADR in the long term. Therefore, this paper recommends consistently reviewing the pension age according to the presented statistical approach. This approach has been used to calculate the target pension age from now until 2060 and its 80% confidence interval. The target pension age found in this research increases to 67 by 2023, 70 by 2032 and 75 by 2058. This generates a stable OADR of around 21%. The rate of growth in the pension age as proposed by the government in 2014 is slightly lower than the target pension age found in this study, which suggests that the government may need to slightly accelerate the growth of the pension age to maintain an OADR at the current level.

The remainder of this paper proceeds as follows. Section 2 reviews key literature on population forecasting and background works on the pension age. Section 3 describes the data and methods used in this study. Section 4 discusses the empirical results of this research, and outlines accuracy tests performed on the empirical results. Finally, Section 6 gives concluding remarks as well as identifies the scope for future research.

# Background and Literature Review

## Background on Australian Age Pension

@@

## Mathematical Preliminaries

### Principal Component Analysis

Principal component analysis (PCA) is the main estimation method used in population forecasting. It is essential for understanding the models introduced in the following sub-section. Therefore, a brief introduction of PCA is given here.

Principal components analysis reorients multivariate data in a way that ensures that the first few dimensions (called components) summarize as much of the available information as possible [@LCG03]. More precisely, it uses an orthogonal transformation  to convert a set of possibly correlated variables into a set of linearly uncorrelated variables called \textit{principal components}. It is possible to reduce the dimensions (new uncorrelated variables) if substantial redundancy is present in the data set. The rearrangement of data allows researchers to decide ``how many principal components to retain for subsequent analysis, trading off simplicity (i.e., a small number of dimensions is easier to manage) against completeness (i.e., a large number of dimensions captures a greater amount of available information)'' [@LCG03, p83].

The mathematical derivation of PCA is explained in detail by @LCG03. I have summarized the main ideas here. In PCA, the objective is to find a linear combination of original data with maximum variance, because the aim is to derive the component (which is the new variable after linear transformation) that summarizes as much information as possible. Suppose we have an $m\times n$ matrix $\bm{X}$ that contains $m$ observations of $n$ variables (dimensions) with a rank of $k$. If we denote linear combinations by the matrix $\bm{U}=[\bm{u_1},\bm{u_2},\bm{u_3},\dots,\bm{u_k}]$ where $\bm{u_i}=(u_{1i},u_{2i},u_{3i},\dots,u_{ni})'$ and denote the matrix of principal component scores by $\bm{Z}=[\bm{z_1},\bm{z_2},\bm{z_3},\dots,\bm{z_k}]$ where $\bm{z_i}=(z_{1i},z_{2i},z_{3i},\dots,z_{mi})'$
, then our goal is to choose $\bm{u_i}$ to maximize the variance of the elements of $\bm{z_i}=\bm{X}\bm{u_i}$, which can be written as:
\begin{equation} 
  var(\bm{z_i})=\frac{1}{m-1}\bm{u_i}' \bm{X}' \bm{X}\bm{u_i}.
\end{equation}
This maximization will ensure that first principal component $\bm{z_1}$ captures the most information (variance) in the original data and every subsequent principal component captures the most information in the remaining variance. However, this maximization does not have a unique solution because the magnitude of $\bm{u}$ is arbitrary, thereby making $var(\bm{z_i})$ infinity. To achieve the maximization, we impose a constraint of unit magnitude on the vector $\bm{u_i} ~\forall i$. Thus, the completed maximization problem is as follows:
\begin{equation}
  \text{choose~} \bm{u} \text{~to maximize~} \frac{1}{m-1}\bm{u}' \bm{X}' \bm{X}\bm{u}
\end{equation}
subject to the constraint $\bm{u}'\bm{u} =1$.

We can solve this constrained optimization problem using the Lagrangian multiplier method (see @LCG03 for a detailed mathematical proof). These authors demonstrate that the solved vectors $\bm{z_i}$ and $\bm{u_i}$ are eigenvectors of the matrices $\bm{X}\bm{X}'$ and $\bm{X}'\bm{X}$ respectively, and the corresponding Lagrangian multiplier $\lambda_i$ is the eigenvalue of $\bm{X}\bm{X}'$. The numbers $\lambda_1,\lambda_2,\dots\lambda_k$ are singular values of $\bm{X}$ and vectors $\bm{z_1},\bm{z_2},\dots,\bm{z_k}$ and $\bm{u_1},\bm{u_2},\dots,\bm{u_k}$ are right and left singular vectors. Also, it can be shown that $\lambda_i$ is equal to $var(\bm{z_i})$, which  implies that variance-covariance matrix of $\bm{Z}$ (denoted by $\Sigma$) is  a diagonal matrix with $\Sigma_{ii}=\lambda_i$. Therefore, the vector $\bm{z}$ associated with largest $\lambda$ is the first principal component, which capture the most variance in original data.

The relationship $\bm{z_i}=\bm{X}\bm{u_i}$ can be written in matrix form as follows:
\begin{equation}
  \bm{Z}=\bm{X}\bm{U}
\end{equation}
With a little algebra, we can rearrange the above equation to express $\bm{X}$ as a function of $\bm{Z}$. We post multiplying $\bm{U}'$ of both sides (note that we have $\bm{U}\bm{U}'=\bm{I}$ because of the mutual orthogonality of eigenvectors) and the new equation is as follows:
\begin{equation}
  \bm{X}=\bm{Z}\bm{U}'
\end{equation}
Further, we can express $\bm{X}$ as a function of standardized matrix of principal components (denoted $\bm{Z_s}$) by decomposing $\bm{Z}$ into $\bm{Z^s}\Sigma^{1/2}$. Then, the equation becomes:
\begin{equation}
  \bm{X}=\bm{Z^s}\Sigma^{1/2}\bm{U}'
\end{equation}
Alternatively, it can be expressed as:
\begin{equation}
  \bm{X}=\bm{z^s_1}\sqrt{\lambda_1}\bm{u_1}'+\bm{z^s_2}\sqrt{\lambda_2}\bm{u_2}'+\dots+\bm{z^s_k}\sqrt{\lambda_k}\bm{u_k}'
\end{equation}
This way of expressing $\bm{X}$ is known as a singular value decomposition (SVD). It indicates that any data matrix $\bm{X}$ can be decomposed into three simpler matrices. $\bm{Z^s}$ is a standardized matrix of uncorrelated variables (each with unit variance), $\Sigma^{1/2}$ is a diagonal matrix which perform a stretching transformation of $\bm{Z^s}$ and $\bm{U}'$ performs an orthogonal rotation. Therefore, we can use singular value decomposition to undertake a PCA.

### ARIMA and ARFIMA Model

ARIMA and ARIFMA are essential mathematical models that is required to understand to perform the population forecasting method. I give a brief introduction of them based on the work of @fpp.

\subparagraph{AR($p$) model}
Autoregression models forecast the dependent variable using a linear combination of its past values. An autoregression model the order of $p$ (referred as AR$(p)$ model) can be written as:
\begin{equation}
y_t=c+\phi_1y_{t-1}+\phi_2y_{t-2}+\dots+\phi_py_{p-1}+e_t
\end{equation}
where $c$ is a constant and $e_t$ is white noise.

\subparagraph{MA(q) model}
A moving average model supposes that the variable of interest can be explained by past forecast errors. It can be written as:
\begin{equation}
y_t=c+e_t+\theta_1e_{t-1}+\theta_2e_{t-2}+\dots+\theta_qe_{t-q}
\end{equation}
where $e_t$ is white noise.

\subparagraph{Non-seasonal ARIMA models}  A non-seasonal ARIMA model is a combination of differencing, autoregression and moveing average models. ARIMA is an acronym for AutoRegressive Integrated Moving Average model. An ARIMA model can be written as:
\begin{equation}
  y_t' = c + \phi_1y_{t-1}' + \dots + \phi_py_{t-p}' + \theta_1e_{t-1} + \dots + \theta_qe_{t-q} + e_t
\end{equation}
where $y_t'$ is the differenced series, which is differenced $d$ times. This regression is referred to as an ARIMA($p,d,q$) model, where $p$ is the order of the auotoregression part; $d$ is the degree of first differencing and $q$ is the order of the moving average part.

In fact, the AR($p$) and MA($q$) models are ARIMA ($p$,0,0) and ARIMA (0,0,$q$) models respectively.
ARIMA models can be written in backshift notation (i.e.$By_t=y_{t-1}$) as follows:
\begin{equation}
  (1-\phi_1B-\dots-\phi_pB^p)(1-B)^dy_t=c+(1+\theta_1B+\dots+\theta_qB^q)e_t
\end{equation}
\subparagraph{ARFIMA model}
We can allow $d$ in the ARIMA model to be fractional in order to capture the long-memory property of some series. The ARIMA model with fractional differencing (i.e., $-\frac{1}{2}<d<\frac{1}{2}$) is called the ARFIMA model. The range $0<d<\frac{1}{2}$ gives long-memory process [@CM09].

\subparagraph{Akaike's Information Criterion}

AIC is a model-selection procedure which is useful to determine the order of an ARIMA model.
It can be written as:
\begin{equation}
  AIC=-2log(L)+2(p+q+k+1)
\end{equation}
where $L$ is the likelihood of the data, $k=1$ if $c\neq0$ and $k=0$ if $c=0$.

For ARIMA models, the corrected AIC [@fpp] can be written as
\begin{equation}
  AIC_c=\frac{AIC+2(p+q+k+1)(p+q+k+2)}{T-p-q-k-2}
\end{equation}
where the correction is to reduce small sample bias.
The ARIMA model with minimum AIC or minimum $AIC_c$ is the optimal model. I prefer to use $AIC_c$ to reduce sample bias in this research.

## Literature Review on Population forecasting methods

@@

# Data and Methodology

## Data

@@

## Methodology

### Forecasting Population Age Structure and OADR

@@

\subparagraph{Step 1}The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast. The @HU07 model, introduced in section 2.3.2, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently. Therefore, to fit the model to historical fertility rates, the $y_t(x)$ in equation (16) denotes the observed historical fertility data. However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13]. In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
\begin{align*}
  p_t(x)=\sqrt{s_{t,M}(x)s_{t,F}(x)},
  r_t(x)=\sqrt{\frac{s_{t,M}(x)}{s_{t,F}(x)}}
\end{align*}
Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
\begin{align*}
  log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$). It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge.
Then, simulation h-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to equation (18) and (19).
From here, obtaining h-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
\begin{align*}
m_{n+h\mid n,M}(x)&=p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
m_{n+h\mid n,F}(x)&=p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
\end{align*}
The method for simulating $h$-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration. A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.

\subparagraph{Step 2} After simulating paths for age-specific fertility rate, age and gender-specific mortality rate and age and gender-specific net migration, future population value were simulated using the demographic growth-balance equations over the prediction horizon. The future deaths and births in this equation are assumed to follow Poisson distribution, with parameters as a function of future mortality and fertility rates (see Hyndman and Booth, 2008 for the details of the functions). Hence, we can simulate $h$-step-ahead age and gender-specific births and deaths based on simulated mortality and fertility rates. According to the demographic growth-balance equation, one-step-ahead net migrations, deaths, births and population in the last year were simulated, allowing for the generation of one-step-ahead population predictions by sex and age. This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a path of population. The process was repeated and simulated $i$ paths of population based on Monte Carlo simulation method were created (we set $i=1000$ in these research). It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in equation (17)), randomness from the ARIMA model fitted to principal component scores and randomness from the Poisson distribution. It should be noted that the simulated population will be an array with 3 dimensions: age, year and simulation.

\subparagraph{Step 3} Even though the OADR is a simple function of the population age structure and pension age, the formula can't be directly applied to the simulated population array because the pension age changes over time. To overcome this problem, we assume that the pension age can only be adjusted at the beginning of a year for these calculations. Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend. I will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2011), given a specific pension age. The same method can be applied to all years over the prediction horizon, given their corresponding pension age. Further, the fractional pension age causes practical issues in calculating OADR, since ages are recorded as integers. I will also show how this issue was handled in the example below.

@@

### Finding the Target Pension Age Scheme

# Empirical Results

## Forecast in Population Age Structure and OADR

@@

@@

## Evaluating Forecast Accuracy

# Conclusions

@@

>>>>

\begin{abstract}
We forecast the old-aged dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old aged dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.

@@

Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the past twenty or so years [@Fehr2008].  Consequently, there are many older people leaving the workforce, and fewer workers replacing them. Similar demographic challenges face many other countries. One way of measuring this problem is via the old-age dependency ratio (OADP): the number of people post-retirement to the number of people of working age [@Walker1982]. The OADP has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.

This is consistent with the Australian Intergenerational Reports [@IGR02; @IGR07; @Swan2010] that explored the extent to which existing age-related policies would affect the burden of future working generations. To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time). In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 [@Nielson2010]. In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035. This new proposal is in line with the recommendations from the @PC13 and the @NCOA2014. In this paper, we investigate the effect of these changes in the pension age on the forecast OADP.

@@

In this paper, we use the old aged dependency ratio as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].  The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age [@ARW07]. This can be expressed using the formula below:
\begin{equation}
  OADR=\frac{\text{number of people aged over pension age}}{\text{number of people aged 15 to pension age}}*100%
\end{equation}
We provide forecasts of future population age structures over the next 50 years. We then use those forecasts to compute the OADR associated with pension age both before and after the adjustments. One contribution of the current study is the combined use of the Hyndman-Ullah forecasting method [@HU07] and the product-ratio method [@HBY13] to forecast a population age structure.  Forecasts of population structure have been built on forecasts of age and gender-specific mortality rates, fertility rates and net migration using this method. These forecasts presuppose that the historical trends of past years will continue. Historical data of those rates have thus been used as input to simulate future paths of age and gender-specific population structure.

Using these predicted population paths, we can calculate the average OADR and predict the levels of old age dependency that correspond to different pension age schemes. By testing different pension age schemes, we aim to find the pension age with the desired OADR outcome. Therefore, other contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2) to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at a desired level in the future. It should be noted that the desired level has been set at 21%, the estimated level of OADR in 2014. Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper. This paper concentrates on providing a framework for policy makers to find a target pension age for a given desired level of OADR.

Some may argue that using OADR as a measure of financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation. However, 80% of Australians over pension age rely fully or partly on the age pension [@Power14]. Therefore, the proportion of people over working age is still a good representation of financial burden on future working generations.  Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors, and @HY12 have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance. We do not consider these here. Our approach is intended to illustrate how population forecasting can be used to explore the pension age issue in a simple context, and it could be extended to take into account other variables.

The remainder of this paper proceeds as follows. Section \@ref(sec:litreview) reviews key literature on population forecasting and the pension age in Australia. Section \@ref(sec:data) describes the data and modelling framework we use in this study.  We show how our framework can be used to estimate a pension age scheme that leads to a target OADR in Section \@ref(sec:target). Finally, Section \@ref(sec:conclusions) gives concluding remarks as well as identifies the scope for future research.

# Background and Literature Review {#sec:litreview}

## The age pension in Australia

@@

## Population forecasting

@@

# Data {#sec:data}

@@

## Forecasting Population Age Structure and OADR {#sec:forecasting}

@@

###Step 1 {-}

The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast. The @HU07 model, introduced in section 2.3.2, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently. Therefore, to fit the model to historical fertility rates, the $y_t(x)$ in equation (16) denotes the observed historical fertility data. However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13]. In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
\begin{align*}
  p_t(x)=\sqrt{s_{t,M}(x)s_{t,F}(x)},
  r_t(x)=\sqrt{\frac{s_{t,M}(x)}{s_{t,F}(x)}}
\end{align*}
Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
\begin{align*}
  log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$). It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge.
Then, simulation h-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to equation (18) and (19).
From here, obtaining h-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
\begin{align*}
m_{n+h\mid n,M}(x)&=p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
m_{n+h\mid n,F}(x)&=p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
\end{align*}
The method for simulating $h$-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration. A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.

### Step 2 {-}

After simulating paths for age-specific fertility rate, age and gender-specific mortality rate and age and gender-specific net migration, future population value were simulated using the demographic growth-balance equations over the prediction horizon. The future deaths and births in this equation are assumed to follow Poisson distribution, with parameters as a function of future mortality and fertility rates (see Hyndman and Booth, 2008 for the details of the functions). Hence, we can simulate $h$-step-ahead age and gender-specific births and deaths based on simulated mortality and fertility rates. According to the demographic growth-balance equation, one-step-ahead net migrations, deaths, births and population in the last year were simulated, allowing for the generation of one-step-ahead population predictions by sex and age. This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a path of population. The process was repeated and simulated $i$ paths of population based on Monte Carlo simulation method were created (we set $i=1000$ in these research). It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in equation (17)), randomness from the ARIMA model fitted to principal component scores and randomness from the Poisson distribution. It should be noted that the simulated population will be an array with 3 dimensions: age, year and simulation.

### Step 3 {-}

Even though the OADR is a simple function of the population age structure and pension age, the formula can't be directly applied to the simulated population array because the pension age changes over time. To overcome this problem, we assume that the pension age can only be adjusted at the beginning of a year for these calculations. Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend. I will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2011), given a specific pension age. The same method can be applied to all years over the prediction horizon, given their corresponding pension age. Further, the fractional pension age causes practical issues in calculating OADR, since ages are recorded as integers. I will also show how this issue was handled in the example below.

@@

## Results

@@

## Evaluating Forecast Accuracy {#sec:accuracy}

# Finding the Target Pension Age Scheme {#sec:target}

@@

# Conclusions {#sec:conclusions}

@@

The empirical analysis presented in this paper shows the adjustment of the pension age announced in 2009 was effective in reducing the financial burden to the desired level, which was set at 21%. However, a one-time adjustment is not sufficient to ensure a stable OADR in the long term, due to ongoing changes in the population age structure. T

herefore, we recommend consistently reviewing the pension age according to the presented statistical approach. This approach has been used to calculate the target pension age from now until 2060 and its 80% confidence interval. The target pension age found in this research increases to 67 by 2023, 70 by 2032 and 75 by 2058. This generates a stable OADR of around 21%. The rate of growth in the pension age as proposed by the government in 2014 is slightly lower than the target pension age found in this study, which suggests that the government may need to slightly accelerate the growth of the pension age to maintain an OADR at the current level.
